Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
writing edits

\begin{enumerate}
\item Memorability: How well do Rewinds facilitate the retrieval of a memory? What types of participants are most likely to recall their memories using Rewinds?
\item Believability:  How accurate are Rewinds in the eyes of the participants? 
\item Desirability: What factors are inherent to participants' decisions in preserving artifacts created by the Rewind system?
\end{enumerate}

@@

Our user study explored the following five metrics as potentially having an effect on memorability, believability, or desirability of digital memory media:
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 corresponded to a range of 10--100 meters; Group 2 corresponded to a range of 100--1,000 meters; Group 3 corresponded to a range of 1,000--10,000 meters; Group 4 corresponded to a range of 10,000--100,000 meters and Group 5 corresponded to a range of 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

@@

%TODO find citation that humans travel most within x km of their home/work nodes
%TODO memory competition--similar memories compete for significance
For Rewind memorability, there was no statistical significance. Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home in Distance Group 1. While remembrance for all distance groups was between 50-60\%, remembrance for Rewinds in Distance Group 1 was 25\%. This data suggests that participants often did not remember or could not distinguish the exact trips that occurred in locations close to their home. This is where most trips happen, and therefore competition between similar memories would make it harder for a person to distinguish the specific trip they were on that generated the Rewind.

@@

%TODO where to put this????  maybe split discussion into three sections on mem/believ/desir
\subsubsection{Episodic Memory}
It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory. Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing Rewinds, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown. Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from Rewinds thereafter.

>>>>

\begin{enumerate}
\item Memorability: How well do Rewinds facilitate the retrieval of a memory? What types of participants are most likely to recall their memories using Rewinds?
\item Believability:  How accurately do Rewinds reflect a person's memory in the eyes of the participants? 
\item Desirability: What factors are inherent to participants' decisions in preserving artifacts created by the Rewind system?
\end{enumerate}

@@

Our user study explored the following five metrics as potentially having an effect on memorability, believability, or desirability of digital memory media:
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

@@

%TODO find citation that humans travel most within x km of their home/work nodes
%TODO memory competition--similar memories compete for significance
For Rewind memorability, there was no statistical significance. Our data does show, however, that Rewind remembrance was largely the same for most distance groups, except for distances that were close to home in Distance Group 1. While remembrance for all distance groups was between 50--60\%, remembrance for Rewinds in Distance Group 1 was 25\%. This data suggests that participants often did not remember or could not distinguish the exact trips that occurred in locations close to their home. This is where most trips happen, and therefore competition between similar memories would make it harder for a person to distinguish the specific trip they were on that generated the Rewind.

@@

%TODO where to put this????  maybe split discussion into three sections on mem/believ/desir
% Jeff thinks that the discussion is already a bit long. It's fine in here, but maybe shorten it. Don't add more sections
\subsection{Episodic Memory}
It could possibly be inferred that participants are likely to benefit more from Rewinds than static street-view images at recalling episodic memory. Although participants were not explicitly asked about trip rememberance when presented with static images as opposed to what they were asked after watchiing Rewinds, location rememberance from static images may serve as an upper-bound estimation of how much an individual could recall about a particular trip; since if participants fail to form any cognitive association with the locations depicted in the images, it is very unlikely that they would be able to associate target itineraries with the locations shown. Thus, it is perhaps safe to presume that location rememberance with images bounds above the maximum likelihood of trip rememberance with the same images presented to the participants, and we used location rememberance from image recognition as an upper-limit gauge against trip rememberance from Rewinds thereafter.
